submission

### 2024-03-08 submission.Rmd

Immediately we can observe that we have significantly less data than for the other exercises, which can indicate that test results can be inconclusive.

>>>>

Immediately we can observe that we have significantly less data than for the other exercises, which can indicate that test results can be inconclusive. To verify how many samples we should have to be able to be able to perform such a test, we can use the power of a t-test. To apply this test we have to understand what

# Perform power analysis
n_active <- 4  # Sample size of the active group
n_inactive <- 9  # Sample size of the inactive group

sp <- sqrt(((n_active-1)*sd(diabetic_active$Glu)**2 + (n_inactive - 1)*sd(diabetic_inactive$Glu)**2**2)/(n_active+n_inactive-2))
effect_size <- (mean(diabetic_active$Glu) - mean(diabetic_inactive$Glu))/sp
alpha <- 0.05  # Significance level

# Perform power analysis
pwr.t.test(n = NULL, d = effect_size, sig.level = alpha, power = 0.5,
                              alternative = "two.sided")
```
